\documentclass[12pt]{article}

\begin{document}

\section{Introduction}
	- "models depict biological processes in simplified and general ways that provide insight into factors that are responsible for observed patterns" (johnson and omland 2004)
	
	- "Temperature is among the most important environmental factors that control plant development, growth and yield. All biological processes respond to temperature, and all responses can be summarized in terms of three cardinal temperatures, namely the base or minimum (Tmin), the optimum (Topt), and the maximum (Tmax) temperatures." (yan and hunt 1999)
	
	- lots of studies on thermal response rates in different contexts, especially important due to climate change, need to know effects.
	- eg. "Climate has a profound effect on the distribution and abundance of invertebrates such as insects, and the mathematical description of the climatic influence on insect development has been of considerable interest among entomologists. " (damos 2012)
	
	- for temp range of photosynthesis see sage 2007
\section{Materials and Methods}
	- use AIC and BIC (And R sqaured) so can compare them
	- briere: used reference to give estimation of starting value for $b_0$ (from briere et al 1999)

\section{Results}
- shape of curves very different - many possibilities
- some flat = temperature range not sufficient to see decline in rate??
- only increasing/decreasing = again could be that temp range not sufficient - MAYBE DO SHCOFIELD UPPER AND LOWER EQUATIONS TO TEST THIS?

- dataset 1, doesn't fit unless you brute force it, calculated value of b0 from equation suggests 0.6 but only value that fits (AIC = 24) is 80,000+
\section{Discussion}

- model selected ultimately depends on the models chosen for the candidate set so if you dont include a model that could best represent the process the could lead to misguided inference (=pitfall)(johnson and omland 2004)

-predictions and parameter estimates must be biologically plausible - check! (johnson + omland 2004)

Validation - the validation of a model isn't to work out whether its 'true', as a model is not a hypothesis and isn't directly verifiable by experiment. Validation is about ensuring the model generates a good testable hypothesis relevant to important problems. (levins 1966)

Unlike the theory, models are constrained to a few components at a time, even if the theory is complex. Therefore, a good theory is usually a cluster of models. (levins 1966)

-briere model doesnt cope if temperature doesnt drop either side of an optimum value

-briere model allows representation of asymmetry around optimum temperature (whereas quad and cubic dont??)
-many models dont include minimum and maximum viable temperatures (t0 and tm) - briere does, schoolfield doesnt (see table 4, briere et al 1999)

\end{document}